---
title: ' '
subtitle: ""

author: ""
date: ''
output:
  html_document:
    df_print: paged
    toc: no
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
nocite: |
link-citations: yes
bibliography: diabetes_citations.bib
editor_options: 
  chunk_output_type: console
csl: biomed-central.csl

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)
```

```{r }
# Importing libraries
library(randomForest)
library(kableExtra)
library(dplyr)
library(caret)
library(C50) # Decision tree


# Set working directory
setwd(dirname(rstudioapi::getSourceEditorContext()$path))
```



<!---### **Summary of predictors in *diabetes* dataset**---> 
```{css}
.main-container {
    max-width: 100%;
}
```

```{r results='hide'}
# Importing the df dataset
diabetes <- read.csv("diabetes.txt", stringsAsFactors = TRUE)
levels(diabetes$diabetes) <- c("Negative", "Positive")

# Performs stratified random split of the data set
set.seed(123)
TrainingIndex <- createDataPartition(diabetes$age, p=0.75, list = FALSE)
TrainingSet <- diabetes[TrainingIndex,] # Training Set
TestingSet <- diabetes[-TrainingIndex,] # Test Set

write.csv(TrainingSet, "training_diabetes.csv")
write.csv(TestingSet, "testing_diabetes.csv")

# Building model_diabetess:

# Random forest model_diabetes
# model_diabetes <- randomForest(TrainingSet$diabetes ~ ., data = TrainingSet, ntree = 500, mtry = 4, importance = TRUE)

# Decision tree
 model_diabetes<- C5.0(TrainingSet[,-9], TrainingSet[,"diabetes"],trials = 10)

# Save model_diabetes to RDS file 
saveRDS(model_diabetes, "model_diabetes.rds")

# model_diabetes predictions
model_diabetes.predict <- predict(model_diabetes,TestingSet) 


# model_diabetes Performance
model_diabetes.performance <- confusionMatrix(data = model_diabetes.predict ,
                reference = TestingSet$diabetes, positive = "Positive")
```

### **Algorithm performance**
This prediction model was built in R using the diabetes data set and the decision tree algorithm C5.0 from the package C50 @KuhnMax2022. The code used to build this predictor and the rest of this Shiny app is available in [GitHub](https://github.com/appropiate/Shiny_apps/tree/main/Shiny_diseases_predictor_RF "Go to www.github.com"). The confusion matrix for the test dataset as well as different performance metrics can be found below:

```{r }

# model_diabetes Performance
(model_diabetes.performance <- confusionMatrix(data = model_diabetes.predict ,
                reference = TestingSet$diabetes, positive = "Positive"))


```

### **References**



